---
title: "Homework 3&4"
author: "Ibrahim Aykut"
date: "19 06 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library("dplyr")
library("lubridate")
library("glmnet")
```

I read file and manipulated the data.
```{r}
aaa=read.csv2("GercekZamanliTuketim-01012016-31052021newnew.csv")
aaa$Tüketim.Miktarı..MWh.=as.numeric(aaa$Tüketim.Miktarı..MWh.)
y1=mutate(aaa,tarih=dmy(Tarih))
```

## Question A

I added lag48 and lag168 values to the data frame and calculated the error.
```{r}
lag48=lag(y1,48)
lag168=lag(y1,168)
new=mutate(y1,lag48tüketim=lag48$Tüketim.Miktarı..MWh.,lag168tüketim=lag168$Tüketim.Miktarı..MWh.,lag48error=(abs((lag48$Tüketim.Miktarı..MWh.-y1$Tüketim.Miktarı..MWh.)/y1$Tüketim.Miktarı..MWh.))*100,lag168error=(abs((lag168$Tüketim.Miktarı..MWh.-y1$Tüketim.Miktarı..MWh.)/y1$Tüketim.Miktarı..MWh.))*100)
```

```{r}
filtre<-filter(new,tarih>=as_date('2021-05-01'))
```

```{r}
summary(filtre$lag48error)
summary(filtre$lag168error)
```

```{r}
quantile(filtre$lag48error,probs = c(0,0.1,0.25,0.5,0.75,0.9))
quantile(filtre$lag168error,probs = c(0,0.1,0.25,0.5,0.75,0.9))
```

```{r}
boxplot(filtre$lag48error)
boxplot(filtre$lag168error)
```

## Question B

I added lag48 and lag168 values to the data frame and gave a row number to each row in order to filter the data.
```{r}
new=mutate(y1,lag48tüketim=lag48$Tüketim.Miktarı..MWh.,lag168tüketim=lag168$Tüketim.Miktarı..MWh.)
new$rownumber=1:nrow(new)
new=filter(new,rownumber>168)
```

I filtered the training and test datasets.
```{r}
trainingdata=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'))
testdata=filter(new,tarih>=as_date('2020-03-01'))
```

I run linear regression for training data.
```{r}
linear_model=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata)
summary(linear_model)
```

I made a prediction for testdata.
```{r}
predicted_model=predict(linear_model,testdata)
```

I calculated MAPE and added them to the dataframe.
```{r}
testdata<-mutate(testdata,MAPE=(abs((testdata$Tüketim.Miktarı..MWh.-predicted_model)/testdata$Tüketim.Miktarı..MWh.)*100))
```

```{r}
summary(testdata$MAPE)
```

## Question C

I manipulated hour values to be able to filter them.
```{r}
y11=y1 %>% mutate(saat=hm(Saat)) %>% mutate(saat=hour(saat))
```

I added lag48 and lag168 values to the data frame.
```{r}
lag48=lag(y11,48)
lag168=lag(y11,168)
new=mutate(y11,lag48tüketim=lag48$Tüketim.Miktarı..MWh.,lag168tüketim=lag168$Tüketim.Miktarı..MWh.)
new$rownumber=1:nrow(new)
new=filter(new,rownumber>168)
```

Training data for each hour.
```{r}
trainingdata0=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==0)
trainingdata1=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==1)
trainingdata2=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==2)
trainingdata3=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==3)
trainingdata4=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==4)
trainingdata5=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==5)
trainingdata6=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==6)
trainingdata7=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==7)
trainingdata8=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==8)
trainingdata9=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==9)
trainingdata10=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==10)
trainingdata11=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==11)
trainingdata12=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==12)
trainingdata13=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==13)
trainingdata14=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==14)
trainingdata15=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==15)
trainingdata16=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==16)
trainingdata17=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==17)
trainingdata18=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==18)
trainingdata19=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==19)
trainingdata20=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==20)
trainingdata21=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==21)
trainingdata22=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==22)
trainingdata23=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==23)
```

Test data for each hour.
```{r}
testdata0=filter(new,tarih>=as_date('2020-03-01'),saat==0)
testdata1=filter(new,tarih>=as_date('2020-03-01'),saat==1)
testdata2=filter(new,tarih>=as_date('2020-03-01'),saat==2)
testdata3=filter(new,tarih>=as_date('2020-03-01'),saat==3)
testdata4=filter(new,tarih>=as_date('2020-03-01'),saat==4)
testdata5=filter(new,tarih>=as_date('2020-03-01'),saat==5)
testdata6=filter(new,tarih>=as_date('2020-03-01'),saat==6)
testdata7=filter(new,tarih>=as_date('2020-03-01'),saat==7)
testdata8=filter(new,tarih>=as_date('2020-03-01'),saat==8)
testdata9=filter(new,tarih>=as_date('2020-03-01'),saat==9)
testdata10=filter(new,tarih>=as_date('2020-03-01'),saat==10)
testdata11=filter(new,tarih>=as_date('2020-03-01'),saat==11)
testdata12=filter(new,tarih>=as_date('2020-03-01'),saat==12)
testdata13=filter(new,tarih>=as_date('2020-03-01'),saat==13)
testdata14=filter(new,tarih>=as_date('2020-03-01'),saat==14)
testdata15=filter(new,tarih>=as_date('2020-03-01'),saat==15)
testdata16=filter(new,tarih>=as_date('2020-03-01'),saat==16)
testdata17=filter(new,tarih>=as_date('2020-03-01'),saat==17)
testdata18=filter(new,tarih>=as_date('2020-03-01'),saat==18)
testdata19=filter(new,tarih>=as_date('2020-03-01'),saat==19)
testdata20=filter(new,tarih>=as_date('2020-03-01'),saat==20)
testdata21=filter(new,tarih>=as_date('2020-03-01'),saat==21)
testdata22=filter(new,tarih>=as_date('2020-03-01'),saat==22)
testdata23=filter(new,tarih>=as_date('2020-03-01'),saat==23)
```

Linear regression for each hour.
```{r}
linear_model0=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata0)
linear_model1=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata1)
linear_model2=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata2)
linear_model3=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata3)
linear_model4=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata4)
linear_model5=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata5)
linear_model6=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata6)
linear_model7=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata7)
linear_model8=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata8)
linear_model9=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata9)
linear_model10=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata10)
linear_model11=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata11)
linear_model12=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata12)
linear_model13=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata13)
linear_model14=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata14)
linear_model15=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata15)
linear_model16=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata16)
linear_model17=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata17)
linear_model18=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata18)
linear_model19=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata19)
linear_model20=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata20)
linear_model21=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata21)
linear_model22=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata22)
linear_model23=lm(Tüketim.Miktarı..MWh.~lag48tüketim+lag168tüketim,data=trainingdata23)
```

Prediction for each hour.
```{r}
predicted_model0=predict(linear_model0,testdata0)
predicted_model1=predict(linear_model1,testdata1)
predicted_model2=predict(linear_model2,testdata2)
predicted_model3=predict(linear_model3,testdata3)
predicted_model4=predict(linear_model4,testdata4)
predicted_model5=predict(linear_model5,testdata5)
predicted_model6=predict(linear_model6,testdata6)
predicted_model7=predict(linear_model7,testdata7)
predicted_model8=predict(linear_model8,testdata8)
predicted_model9=predict(linear_model9,testdata9)
predicted_model10=predict(linear_model10,testdata10)
predicted_model11=predict(linear_model11,testdata11)
predicted_model12=predict(linear_model12,testdata12)
predicted_model13=predict(linear_model13,testdata13)
predicted_model14=predict(linear_model14,testdata14)
predicted_model15=predict(linear_model15,testdata15)
predicted_model16=predict(linear_model16,testdata16)
predicted_model17=predict(linear_model17,testdata17)
predicted_model18=predict(linear_model18,testdata18)
predicted_model19=predict(linear_model19,testdata19)
predicted_model20=predict(linear_model20,testdata20)
predicted_model21=predict(linear_model20,testdata21)
predicted_model22=predict(linear_model20,testdata22)
predicted_model23=predict(linear_model20,testdata23)
```

I calculated MAPE and added them to the dataframe.
```{r}
testdata0<-mutate(testdata0,MAPE=(abs((testdata0$Tüketim.Miktarı..MWh.-predicted_model0)/testdata0$Tüketim.Miktarı..MWh.)*100))
testdata1<-mutate(testdata1,MAPE=(abs((testdata1$Tüketim.Miktarı..MWh.-predicted_model1)/testdata1$Tüketim.Miktarı..MWh.)*100))
testdata2<-mutate(testdata2,MAPE=(abs((testdata2$Tüketim.Miktarı..MWh.-predicted_model2)/testdata2$Tüketim.Miktarı..MWh.)*100))
testdata3<-mutate(testdata3,MAPE=(abs((testdata3$Tüketim.Miktarı..MWh.-predicted_model3)/testdata3$Tüketim.Miktarı..MWh.)*100))
testdata4<-mutate(testdata4,MAPE=(abs((testdata4$Tüketim.Miktarı..MWh.-predicted_model4)/testdata4$Tüketim.Miktarı..MWh.)*100))
testdata5<-mutate(testdata5,MAPE=(abs((testdata5$Tüketim.Miktarı..MWh.-predicted_model5)/testdata5$Tüketim.Miktarı..MWh.)*100))
testdata6<-mutate(testdata6,MAPE=(abs((testdata6$Tüketim.Miktarı..MWh.-predicted_model6)/testdata6$Tüketim.Miktarı..MWh.)*100))
testdata7<-mutate(testdata7,MAPE=(abs((testdata7$Tüketim.Miktarı..MWh.-predicted_model7)/testdata7$Tüketim.Miktarı..MWh.)*100))
testdata8<-mutate(testdata8,MAPE=(abs((testdata8$Tüketim.Miktarı..MWh.-predicted_model8)/testdata8$Tüketim.Miktarı..MWh.)*100))
testdata9<-mutate(testdata9,MAPE=(abs((testdata9$Tüketim.Miktarı..MWh.-predicted_model9)/testdata9$Tüketim.Miktarı..MWh.)*100))
testdata10<-mutate(testdata10,MAPE=(abs((testdata10$Tüketim.Miktarı..MWh.-predicted_model10)/testdata10$Tüketim.Miktarı..MWh.)*100))
testdata11<-mutate(testdata11,MAPE=(abs((testdata11$Tüketim.Miktarı..MWh.-predicted_model11)/testdata11$Tüketim.Miktarı..MWh.)*100))
testdata12<-mutate(testdata12,MAPE=(abs((testdata12$Tüketim.Miktarı..MWh.-predicted_model12)/testdata12$Tüketim.Miktarı..MWh.)*100))
testdata13<-mutate(testdata13,MAPE=(abs((testdata13$Tüketim.Miktarı..MWh.-predicted_model13)/testdata13$Tüketim.Miktarı..MWh.)*100))
testdata14<-mutate(testdata14,MAPE=(abs((testdata14$Tüketim.Miktarı..MWh.-predicted_model14)/testdata14$Tüketim.Miktarı..MWh.)*100))
testdata15<-mutate(testdata15,MAPE=(abs((testdata15$Tüketim.Miktarı..MWh.-predicted_model15)/testdata15$Tüketim.Miktarı..MWh.)*100))
testdata16<-mutate(testdata16,MAPE=(abs((testdata16$Tüketim.Miktarı..MWh.-predicted_model16)/testdata16$Tüketim.Miktarı..MWh.)*100))
testdata17<-mutate(testdata17,MAPE=(abs((testdata17$Tüketim.Miktarı..MWh.-predicted_model17)/testdata17$Tüketim.Miktarı..MWh.)*100))
testdata18<-mutate(testdata18,MAPE=(abs((testdata18$Tüketim.Miktarı..MWh.-predicted_model18)/testdata18$Tüketim.Miktarı..MWh.)*100))
testdata19<-mutate(testdata19,MAPE=(abs((testdata19$Tüketim.Miktarı..MWh.-predicted_model19)/testdata19$Tüketim.Miktarı..MWh.)*100))
testdata20<-mutate(testdata20,MAPE=(abs((testdata20$Tüketim.Miktarı..MWh.-predicted_model20)/testdata20$Tüketim.Miktarı..MWh.)*100))
testdata21<-mutate(testdata21,MAPE=(abs((testdata21$Tüketim.Miktarı..MWh.-predicted_model21)/testdata21$Tüketim.Miktarı..MWh.)*100))
testdata22<-mutate(testdata22,MAPE=(abs((testdata22$Tüketim.Miktarı..MWh.-predicted_model22)/testdata22$Tüketim.Miktarı..MWh.)*100))
testdata23<-mutate(testdata23,MAPE=(abs((testdata23$Tüketim.Miktarı..MWh.-predicted_model23)/testdata23$Tüketim.Miktarı..MWh.)*100))

```

Summary of MAPE values.
```{r}
summary(testdata0$MAPE)
summary(testdata1$MAPE)
summary(testdata2$MAPE)
summary(testdata3$MAPE)
summary(testdata4$MAPE)
summary(testdata5$MAPE)
summary(testdata6$MAPE)
summary(testdata7$MAPE)
summary(testdata8$MAPE)
summary(testdata9$MAPE)
summary(testdata10$MAPE)
summary(testdata11$MAPE)
summary(testdata12$MAPE)
summary(testdata13$MAPE)
summary(testdata14$MAPE)
summary(testdata15$MAPE)
summary(testdata16$MAPE)
summary(testdata17$MAPE)
summary(testdata18$MAPE)
summary(testdata19$MAPE)
summary(testdata20$MAPE)
summary(testdata21$MAPE)
summary(testdata22$MAPE)
summary(testdata23$MAPE)
```


## Question D

I got 2 days ago's electrical consumption for each hour.
```{r}
lag48_0=lag(y11,48)
lag48_1=lag(y11,47)
lag48_2=lag(y11,46)
lag48_3=lag(y11,45)
lag48_4=lag(y11,44)
lag48_5=lag(y11,43)
lag48_6=lag(y11,42)
lag48_7=lag(y11,41)
lag48_8=lag(y11,40)
lag48_9=lag(y11,39)
lag48_10=lag(y11,38)
lag48_11=lag(y11,37)
lag48_12=lag(y11,36)
lag48_13=lag(y11,35)
lag48_14=lag(y11,34)
lag48_15=lag(y11,33)
lag48_16=lag(y11,32)
lag48_17=lag(y11,31)
lag48_18=lag(y11,30)
lag48_19=lag(y11,29)
lag48_20=lag(y11,28)
lag48_21=lag(y11,27)
lag48_22=lag(y11,26)
lag48_23=lag(y11,25)
```

I got last week's electrical consumption for each hour.
```{r}
lag168_0=lag(y11,168)
lag168_1=lag(y11,167)
lag168_2=lag(y11,166)
lag168_3=lag(y11,165)
lag168_4=lag(y11,164)
lag168_5=lag(y11,163)
lag168_6=lag(y11,162)
lag168_7=lag(y11,161)
lag168_8=lag(y11,160)
lag168_9=lag(y11,159)
lag168_10=lag(y11,158)
lag168_11=lag(y11,157)
lag168_12=lag(y11,156)
lag168_13=lag(y11,155)
lag168_14=lag(y11,154)
lag168_15=lag(y11,153)
lag168_16=lag(y11,152)
lag168_17=lag(y11,151)
lag168_18=lag(y11,150)
lag168_19=lag(y11,149)
lag168_20=lag(y11,148)
lag168_21=lag(y11,147)
lag168_22=lag(y11,146)
lag168_23=lag(y11,145)
```

I added them as a feature to the dataframe.
```{r}
new=mutate(y11,lag48_0tüketim=lag48_0$Tüketim.Miktarı..MWh.,lag48_1tüketim=lag48_1$Tüketim.Miktarı..MWh.,lag48_2tüketim=lag48_2$Tüketim.Miktarı..MWh.,lag48_3tüketim=lag48_3$Tüketim.Miktarı..MWh.,y11,lag48_4tüketim=lag48_4$Tüketim.Miktarı..MWh.,lag48_5tüketim=lag48_5$Tüketim.Miktarı..MWh.,lag48_6tüketim=lag48_6$Tüketim.Miktarı..MWh.,lag48_7tüketim=lag48_7$Tüketim.Miktarı..MWh.,lag48_8tüketim=lag48_8$Tüketim.Miktarı..MWh.,lag48_9tüketim=lag48_9$Tüketim.Miktarı..MWh.,lag48_10tüketim=lag48_10$Tüketim.Miktarı..MWh.,
           lag48_11tüketim=lag48_11$Tüketim.Miktarı..MWh.,lag48_12tüketim=lag48_12$Tüketim.Miktarı..MWh.,lag48_13tüketim=lag48_13$Tüketim.Miktarı..MWh.,lag48_14tüketim=lag48_14$Tüketim.Miktarı..MWh.,lag48_15tüketim=lag48_15$Tüketim.Miktarı..MWh.,lag48_16tüketim=lag48_16$Tüketim.Miktarı..MWh.,lag48_17tüketim=lag48_17$Tüketim.Miktarı..MWh.,lag48_18tüketim=lag48_18$Tüketim.Miktarı..MWh.,lag48_19tüketim=lag48_19$Tüketim.Miktarı..MWh.,lag48_20tüketim=lag48_20$Tüketim.Miktarı..MWh.,
           lag48_21tüketim=lag48_21$Tüketim.Miktarı..MWh.,lag48_22tüketim=lag48_22$Tüketim.Miktarı..MWh.,lag48_23tüketim=lag48_23$Tüketim.Miktarı..MWh.,
           y11,lag168_0tüketim=lag168_0$Tüketim.Miktarı..MWh.,lag168_1tüketim=lag168_1$Tüketim.Miktarı..MWh.,lag168_2tüketim=lag168_2$Tüketim.Miktarı..MWh.,lag168_3tüketim=lag168_3$Tüketim.Miktarı..MWh.,y11,lag168_4tüketim=lag168_4$Tüketim.Miktarı..MWh.,lag168_5tüketim=lag168_5$Tüketim.Miktarı..MWh.,lag168_6tüketim=lag168_6$Tüketim.Miktarı..MWh.,lag168_7tüketim=lag168_7$Tüketim.Miktarı..MWh.,lag168_8tüketim=lag168_8$Tüketim.Miktarı..MWh.,lag168_9tüketim=lag168_9$Tüketim.Miktarı..MWh.,lag168_10tüketim=lag168_10$Tüketim.Miktarı..MWh.,
           lag168_11tüketim=lag168_11$Tüketim.Miktarı..MWh.,lag168_12tüketim=lag168_12$Tüketim.Miktarı..MWh.,lag168_13tüketim=lag168_13$Tüketim.Miktarı..MWh.,lag168_14tüketim=lag168_14$Tüketim.Miktarı..MWh.,lag168_15tüketim=lag168_15$Tüketim.Miktarı..MWh.,lag168_16tüketim=lag168_16$Tüketim.Miktarı..MWh.,lag168_17tüketim=lag168_17$Tüketim.Miktarı..MWh.,lag168_18tüketim=lag168_18$Tüketim.Miktarı..MWh.,lag168_19tüketim=lag168_19$Tüketim.Miktarı..MWh.,lag168_20tüketim=lag168_20$Tüketim.Miktarı..MWh.,
           lag168_21tüketim=lag168_21$Tüketim.Miktarı..MWh.,lag168_22tüketim=lag168_22$Tüketim.Miktarı..MWh.,lag168_23tüketim=lag168_23$Tüketim.Miktarı..MWh.)

```

```{r}
new$rownumber=1:nrow(new)
new=filter(new,rownumber>168)
```

Training data for each hour.
```{r}
trainingdata0=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==0)
trainingdata1=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==1)
trainingdata2=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==2)
trainingdata3=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==3)
trainingdata4=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==4)
trainingdata5=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==5)
trainingdata6=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==6)
trainingdata7=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==7)
trainingdata8=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==8)
trainingdata9=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==9)
trainingdata10=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==10)
trainingdata11=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==11)
trainingdata12=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==12)
trainingdata13=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==13)
trainingdata14=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==14)
trainingdata15=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==15)
trainingdata16=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==16)
trainingdata17=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==17)
trainingdata18=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==18)
trainingdata19=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==19)
trainingdata20=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==20)
trainingdata21=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==21)
trainingdata22=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==22)
trainingdata23=filter(new,tarih>=as_date('2016-01-08'),tarih<as_date('2020-03-01'),saat==23)
```

Test data for each hour.
```{r}
testdata0=filter(new,tarih>=as_date('2020-03-01'),saat==0)
testdata1=filter(new,tarih>=as_date('2020-03-01'),saat==1)
testdata2=filter(new,tarih>=as_date('2020-03-01'),saat==2)
testdata3=filter(new,tarih>=as_date('2020-03-01'),saat==3)
testdata4=filter(new,tarih>=as_date('2020-03-01'),saat==4)
testdata5=filter(new,tarih>=as_date('2020-03-01'),saat==5)
testdata6=filter(new,tarih>=as_date('2020-03-01'),saat==6)
testdata7=filter(new,tarih>=as_date('2020-03-01'),saat==7)
testdata8=filter(new,tarih>=as_date('2020-03-01'),saat==8)
testdata9=filter(new,tarih>=as_date('2020-03-01'),saat==9)
testdata10=filter(new,tarih>=as_date('2020-03-01'),saat==10)
testdata11=filter(new,tarih>=as_date('2020-03-01'),saat==11)
testdata12=filter(new,tarih>=as_date('2020-03-01'),saat==12)
testdata13=filter(new,tarih>=as_date('2020-03-01'),saat==13)
testdata14=filter(new,tarih>=as_date('2020-03-01'),saat==14)
testdata15=filter(new,tarih>=as_date('2020-03-01'),saat==15)
testdata16=filter(new,tarih>=as_date('2020-03-01'),saat==16)
testdata17=filter(new,tarih>=as_date('2020-03-01'),saat==17)
testdata18=filter(new,tarih>=as_date('2020-03-01'),saat==18)
testdata19=filter(new,tarih>=as_date('2020-03-01'),saat==19)
testdata20=filter(new,tarih>=as_date('2020-03-01'),saat==20)
testdata21=filter(new,tarih>=as_date('2020-03-01'),saat==21)
testdata22=filter(new,tarih>=as_date('2020-03-01'),saat==22)
testdata23=filter(new,tarih>=as_date('2020-03-01'),saat==23)
```

Lasso regression for each hour.
```{r}
cv_fit0=cv.glmnet(data.matrix(trainingdata0[,-c(1,2,3,4,5,54)]),trainingdata0$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit1=cv.glmnet(data.matrix(trainingdata1[,-c(1,2,3,4,5,54)]),trainingdata1$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit2=cv.glmnet(data.matrix(trainingdata2[,-c(1,2,3,4,5,54)]),trainingdata2$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit3=cv.glmnet(data.matrix(trainingdata3[,-c(1,2,3,4,5,54)]),trainingdata3$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit4=cv.glmnet(data.matrix(trainingdata4[,-c(1,2,3,4,5,54)]),trainingdata4$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit5=cv.glmnet(data.matrix(trainingdata5[,-c(1,2,3,4,5,54)]),trainingdata5$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit6=cv.glmnet(data.matrix(trainingdata6[,-c(1,2,3,4,5,54)]),trainingdata6$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit7=cv.glmnet(data.matrix(trainingdata7[,-c(1,2,3,4,5,54)]),trainingdata7$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit8=cv.glmnet(data.matrix(trainingdata8[,-c(1,2,3,4,5,54)]),trainingdata8$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit9=cv.glmnet(data.matrix(trainingdata9[,-c(1,2,3,4,5,54)]),trainingdata9$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit10=cv.glmnet(data.matrix(trainingdata10[,-c(1,2,3,4,5,54)]),trainingdata10$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit11=cv.glmnet(data.matrix(trainingdata11[,-c(1,2,3,4,5,54)]),trainingdata11$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit12=cv.glmnet(data.matrix(trainingdata12[,-c(1,2,3,4,5,54)]),trainingdata12$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit13=cv.glmnet(data.matrix(trainingdata13[,-c(1,2,3,4,5,54)]),trainingdata13$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit14=cv.glmnet(data.matrix(trainingdata14[,-c(1,2,3,4,5,54)]),trainingdata14$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit15=cv.glmnet(data.matrix(trainingdata15[,-c(1,2,3,4,5,54)]),trainingdata15$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit16=cv.glmnet(data.matrix(trainingdata16[,-c(1,2,3,4,5,54)]),trainingdata16$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit17=cv.glmnet(data.matrix(trainingdata17[,-c(1,2,3,4,5,54)]),trainingdata17$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit18=cv.glmnet(data.matrix(trainingdata18[,-c(1,2,3,4,5,54)]),trainingdata18$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit19=cv.glmnet(data.matrix(trainingdata19[,-c(1,2,3,4,5,54)]),trainingdata19$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit20=cv.glmnet(data.matrix(trainingdata20[,-c(1,2,3,4,5,54)]),trainingdata20$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit21=cv.glmnet(data.matrix(trainingdata21[,-c(1,2,3,4,5,54)]),trainingdata21$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit22=cv.glmnet(data.matrix(trainingdata22[,-c(1,2,3,4,5,54)]),trainingdata22$Tüketim.Miktarı..MWh.,family="gaussian")
cv_fit23=cv.glmnet(data.matrix(trainingdata23[,-c(1,2,3,4,5,54)]),trainingdata23$Tüketim.Miktarı..MWh.,family="gaussian")

```

Plots and coefficient of each regression model.
```{r}
plot(cv_fit0)
coef(cv_fit0,s='lambda.1se')
plot(cv_fit1)
coef(cv_fit1,s='lambda.1se')
plot(cv_fit2)
coef(cv_fit2,s='lambda.1se')
plot(cv_fit3)
coef(cv_fit3,s='lambda.1se')
plot(cv_fit4)
coef(cv_fit4,s='lambda.1se')
plot(cv_fit5)
coef(cv_fit5,s='lambda.1se')
plot(cv_fit6)
coef(cv_fit6,s='lambda.1se')
plot(cv_fit7)
coef(cv_fit7,s='lambda.1se')
plot(cv_fit8)
coef(cv_fit8,s='lambda.1se')
plot(cv_fit9)
coef(cv_fit9,s='lambda.1se')
plot(cv_fit10)
coef(cv_fit10,s='lambda.1se')
plot(cv_fit11)
coef(cv_fit11,s='lambda.1se')
plot(cv_fit12)
coef(cv_fit12,s='lambda.1se')
plot(cv_fit13)
coef(cv_fit13,s='lambda.1se')
plot(cv_fit14)
coef(cv_fit14,s='lambda.1se')
plot(cv_fit15)
coef(cv_fit15,s='lambda.1se')
plot(cv_fit16)
coef(cv_fit16,s='lambda.1se')
plot(cv_fit17)
coef(cv_fit17,s='lambda.1se')
plot(cv_fit18)
coef(cv_fit18,s='lambda.1se')
plot(cv_fit19)
coef(cv_fit19,s='lambda.1se')
plot(cv_fit20)
coef(cv_fit20,s='lambda.1se')
plot(cv_fit21)
coef(cv_fit21,s='lambda.1se')
plot(cv_fit22)
coef(cv_fit22,s='lambda.1se')
plot(cv_fit23)
coef(cv_fit23,s='lambda.1se')
```

Prediction for each hour.
```{r}
predicted_model0=predict(cv_fit0,data.matrix(testdata0[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model1=predict(cv_fit1,data.matrix(testdata1[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model2=predict(cv_fit2,data.matrix(testdata2[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model3=predict(cv_fit3,data.matrix(testdata3[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model4=predict(cv_fit4,data.matrix(testdata4[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model5=predict(cv_fit5,data.matrix(testdata5[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model6=predict(cv_fit6,data.matrix(testdata6[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model7=predict(cv_fit7,data.matrix(testdata7[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model8=predict(cv_fit8,data.matrix(testdata8[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model9=predict(cv_fit9,data.matrix(testdata9[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model10=predict(cv_fit10,data.matrix(testdata10[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model11=predict(cv_fit11,data.matrix(testdata11[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model12=predict(cv_fit12,data.matrix(testdata12[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model13=predict(cv_fit13,data.matrix(testdata13[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model14=predict(cv_fit14,data.matrix(testdata14[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model15=predict(cv_fit15,data.matrix(testdata15[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model16=predict(cv_fit16,data.matrix(testdata16[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model17=predict(cv_fit17,data.matrix(testdata17[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model18=predict(cv_fit18,data.matrix(testdata18[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model19=predict(cv_fit19,data.matrix(testdata19[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model20=predict(cv_fit20,data.matrix(testdata20[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model21=predict(cv_fit21,data.matrix(testdata21[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model22=predict(cv_fit22,data.matrix(testdata22[,-c(1,2,3,4,5,54)]),s='lambda.min')
predicted_model23=predict(cv_fit23,data.matrix(testdata23[,-c(1,2,3,4,5,54)]),s='lambda.min')
```

I calculated MAPE and added them to the dataframe.
```{r}
testdata0<-mutate(testdata0,MAPE=(abs((testdata0$Tüketim.Miktarı..MWh.-predicted_model0)/testdata0$Tüketim.Miktarı..MWh.)*100))
testdata1<-mutate(testdata1,MAPE=(abs((testdata1$Tüketim.Miktarı..MWh.-predicted_model1)/testdata1$Tüketim.Miktarı..MWh.)*100))
testdata2<-mutate(testdata2,MAPE=(abs((testdata2$Tüketim.Miktarı..MWh.-predicted_model2)/testdata2$Tüketim.Miktarı..MWh.)*100))
testdata3<-mutate(testdata3,MAPE=(abs((testdata3$Tüketim.Miktarı..MWh.-predicted_model3)/testdata3$Tüketim.Miktarı..MWh.)*100))
testdata4<-mutate(testdata4,MAPE=(abs((testdata4$Tüketim.Miktarı..MWh.-predicted_model4)/testdata4$Tüketim.Miktarı..MWh.)*100))
testdata5<-mutate(testdata5,MAPE=(abs((testdata5$Tüketim.Miktarı..MWh.-predicted_model5)/testdata5$Tüketim.Miktarı..MWh.)*100))
testdata6<-mutate(testdata6,MAPE=(abs((testdata6$Tüketim.Miktarı..MWh.-predicted_model6)/testdata6$Tüketim.Miktarı..MWh.)*100))
testdata7<-mutate(testdata7,MAPE=(abs((testdata7$Tüketim.Miktarı..MWh.-predicted_model7)/testdata7$Tüketim.Miktarı..MWh.)*100))
testdata8<-mutate(testdata8,MAPE=(abs((testdata8$Tüketim.Miktarı..MWh.-predicted_model8)/testdata8$Tüketim.Miktarı..MWh.)*100))
testdata9<-mutate(testdata9,MAPE=(abs((testdata9$Tüketim.Miktarı..MWh.-predicted_model9)/testdata9$Tüketim.Miktarı..MWh.)*100))
testdata10<-mutate(testdata10,MAPE=(abs((testdata10$Tüketim.Miktarı..MWh.-predicted_model10)/testdata10$Tüketim.Miktarı..MWh.)*100))
testdata11<-mutate(testdata11,MAPE=(abs((testdata11$Tüketim.Miktarı..MWh.-predicted_model11)/testdata11$Tüketim.Miktarı..MWh.)*100))
testdata12<-mutate(testdata12,MAPE=(abs((testdata12$Tüketim.Miktarı..MWh.-predicted_model12)/testdata12$Tüketim.Miktarı..MWh.)*100))
testdata13<-mutate(testdata13,MAPE=(abs((testdata13$Tüketim.Miktarı..MWh.-predicted_model13)/testdata13$Tüketim.Miktarı..MWh.)*100))
testdata14<-mutate(testdata14,MAPE=(abs((testdata14$Tüketim.Miktarı..MWh.-predicted_model14)/testdata14$Tüketim.Miktarı..MWh.)*100))
testdata15<-mutate(testdata15,MAPE=(abs((testdata15$Tüketim.Miktarı..MWh.-predicted_model15)/testdata15$Tüketim.Miktarı..MWh.)*100))
testdata16<-mutate(testdata16,MAPE=(abs((testdata16$Tüketim.Miktarı..MWh.-predicted_model16)/testdata16$Tüketim.Miktarı..MWh.)*100))
testdata17<-mutate(testdata17,MAPE=(abs((testdata17$Tüketim.Miktarı..MWh.-predicted_model17)/testdata17$Tüketim.Miktarı..MWh.)*100))
testdata18<-mutate(testdata18,MAPE=(abs((testdata18$Tüketim.Miktarı..MWh.-predicted_model18)/testdata18$Tüketim.Miktarı..MWh.)*100))
testdata19<-mutate(testdata19,MAPE=(abs((testdata19$Tüketim.Miktarı..MWh.-predicted_model19)/testdata19$Tüketim.Miktarı..MWh.)*100))
testdata20<-mutate(testdata20,MAPE=(abs((testdata20$Tüketim.Miktarı..MWh.-predicted_model20)/testdata20$Tüketim.Miktarı..MWh.)*100))
testdata21<-mutate(testdata21,MAPE=(abs((testdata21$Tüketim.Miktarı..MWh.-predicted_model21)/testdata21$Tüketim.Miktarı..MWh.)*100))
testdata22<-mutate(testdata22,MAPE=(abs((testdata22$Tüketim.Miktarı..MWh.-predicted_model22)/testdata22$Tüketim.Miktarı..MWh.)*100))
testdata23<-mutate(testdata23,MAPE=(abs((testdata23$Tüketim.Miktarı..MWh.-predicted_model23)/testdata23$Tüketim.Miktarı..MWh.)*100))

```

Summary of MAPE values.
```{r}
summary(testdata0$MAPE)
summary(testdata1$MAPE)
summary(testdata2$MAPE)
summary(testdata3$MAPE)
summary(testdata4$MAPE)
summary(testdata5$MAPE)
summary(testdata6$MAPE)
summary(testdata7$MAPE)
summary(testdata8$MAPE)
summary(testdata9$MAPE)
summary(testdata10$MAPE)
summary(testdata11$MAPE)
summary(testdata12$MAPE)
summary(testdata13$MAPE)
summary(testdata14$MAPE)
summary(testdata15$MAPE)
summary(testdata16$MAPE)
summary(testdata17$MAPE)
summary(testdata18$MAPE)
summary(testdata19$MAPE)
summary(testdata20$MAPE)
summary(testdata21$MAPE)
summary(testdata22$MAPE)
summary(testdata23$MAPE)
```

